Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-11-02 scagnostics.Rmd
re-working null path images

```{r plotV1V2toV3V4, fig.width=6, fig.height=7, fig.cap="Short tour paths of uninformed views, moving from the projection onto $x_1$-$x_2$ to the projection onto $x_3$-$x_4$, for all considered datasets and index functions. Small samples (n=100) are shown in red, large samples (n=1000) in blue."}
fullResMelt <- melt(fullRes, id=c("t", "name", "size"))
ggplot(fullResMelt, aes(x=t, y=value)) +
  geom_line(aes(color=factor(size))) + 
  facet_wrap(variable~name, ncol=3, scales = "free_y", labeller = label_wrap_gen(multi_line=FALSE)) +
  guides(color=FALSE)
```

>>>>

```{r plotV1V2toV3V4, fig.width=6, fig.height=7, fig.cap="Short tour paths of uninformed views, moving from the projection onto $x_1$-$x_2$ to the projection onto $x_3$-$x_4$, for all considered datasets and index functions. Small samples (n=100) are shown in red, large samples (n=1000) in blue."}
fullResMelt <- fullRes %>% gather(PPI, value, -t, -name, -size)
#ggplot(fullResMelt, aes(x=t, y=value)) +
#  geom_line(aes(color=factor(size))) + 
#  facet_wrap(variable~name, ncol=3, scales = "free_y", labeller = label_wrap_gen(multi_line=FALSE)) +
#  guides(color=FALSE)
fullResMelt %>% 
  ggplot(aes(x=t, y=value)) + 
  geom_line(aes(group=size, linetype=factor(size, levels=c("1000", "100")))) + 
  ylim(c(0,1)) +
  facet_grid(PPI~name) + 
  theme(legend.position="none")
```
